%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Marcel Hofmann}} & Email : \href{mailto:marcel.hofmann@hofmania.de}{marcel.hofmann@hofmania.de}\\
  \href{https://github.com/marcelhfm}{https://github.com/marcelhfm} & Mobile : +4917660335763 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of applied sciences Munich}{München, Germany}
      {Bachelor of Science in Business Informatics;  current GPA: 1.4}{2020 -- 2024}
    \resumeSubheading
      {University of Halmstad}{Halmstad, Sweden}
      {ERASMUS Semester Abroad}{2023}
    \resumeSubheading
      {Josef Effner-Gymnasium Dachau}{Dachau, Germany}
      {A-Levels (Abitur); GPA: 1.8}{2012-2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Codestryke}{München, Germany}
      {Full Stack Engineer}{2022 - present}
      \resumeItemListStart
        \resumeItem{Lead Backend Developer for an insurance based IoT-Platform}
          {Responsibility for highly scalable IoT data ingestion, preprocessing and analysis. Developing a rule engine for real-time event generation and alerting. Automated E2E and load testing using Azure DevOps Pipelines. Deployment on Azure using k8s and Azure Functions. (MQTT, REST, GraphQl, Node, Typescript)}
        \resumeItem{Lead Full Stack Developer for an IoT-Monitoring Dashboard}
          {Real-time monitoring and timeseries data analysis. Deployment on Mindsphere (Siemens IoT-Platform) and AWS using Lambda. (GraphQl, REST, Node, Typescript, React)}
      \resumeItemListEnd

    \resumeSubheading
      {Siemens Health Insurance}{München, Germany}
      {Working Student Project Management}{2021 - 2022}
      \resumeItemListStart
        \resumeItem{Project Management App and Web}
          {UI and UX research. Testing. Coordination of projects.}
      \resumeItemListEnd

   \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Raspberry Pi Pico W - CO2 Sensor (ongoing)}
      {Real-Time Data collection using a C02 sensor and displaying it with an OLED-Display. Developed in C using FreeRTOS. (I2C, MQTT)}
    \resumeSubItem{PIOS - Simple OS for the Raspberry Pi 4b (ongoing)}
      {Simple Operating System from scratch. Implementing user interfaces with UART and bluetooth. (C, ASM)}
    \resumeSubItem{TCP / UDP Chat Messenger}
      {University Project. Scalable End-2-End communication with TCP/IP or UDP/IP. (Java)}
    \resumeSubItem{FOREX trading bot}
   	 {Automated python trading bot. (Python)}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     	\textbf{Languages}{: Typescript, Javascript, C, C++, C\#, Java, Python}
        }
   \item{
   		\textbf{Technologies}{: AWS, Azure, Node, React, Kubernetes}
   		}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
